Combining language resources into a grammar-driven Swedish parser

### 2011-10-24 doc/paper/Paper.tex
latest paper

\begin{abstract}
This paper describes on-going work of a rule-based, open-source
parser for Swedish. The central component is a wide-coverage grammar
implemented in the Grammatical Framework formalism (GF), from which
we obtain a %can be compiled to a % from which we derive?? 
parser.
In addition to GF, we use two other main resources: the Swedish
treebank Talbanken and the electronic SALDO lexicon.
The resulting parser 
gives a full syntactic analysis of the input sentences.
It will be highly reusable, freely available,
and as GF provides libraries for compiling
grammars to a number of programming languages,
chosen parts of the the 
grammar may be used in various NLP applications. % dealing with
%controlled or free
%natural language. 
% allow easy interaction with other programs and grammars
%>> something very commercial, interesting and outstanding here please!

>>>>

\begin{abstract}
This paper describes on-going work on a rule-based, open-source
parser for Swedish. The central component is a wide-coverage grammar
implemented in the GF formalism (Grammatical Framework), from which
we obtain a %can be compiled to a % from which we derive?? 
parser.
In addition to GF, we use two other main resources: the Swedish
treebank Talbanken and the electronic SALDO lexicon.
The resulting parser 
gives a full syntactic analysis of the input sentences.
It will be highly reusable, freely available,
and as GF provides libraries for compiling
grammars to a number of programming languages,
chosen parts of the the 
grammar may be used in various NLP applications. % dealing with
%controlled or free
%natural language. 
% allow easy interaction with other programs and grammars
%>> something very commercial, interesting and outstanding here please!
